Learning Discrete Bayesian Networks from Continuous Data

### 2016-08-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
cited 4 BayesBlocks related papers and added some sentences to prior 1 discussion

A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or to use field-specific expertise.
A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.
The MDL principle proposed by \cite{MDL_1978} states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and the optimal positions of their discretization edges.
Their approach selects a discretization policy that minimizes the sum of the description length of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.

@@

where $L$ is the largest number of intervals among discrete variables in $\cX$'s Markov blanket.
This encourages edges between well-separated values over edges between closely packed samples.

>>>>

A common discretization method for Bayesian networks is to split continuous variables into uniform-width intervals or to use field-specific expertise \citep{scott1979optimal, freedman1981histogram, knuth2013optimal, scargle2013studies}.
A more principled method is the minimum description length (MDL) principle discretization \citep{Friedman_1996}.
The MDL principle proposed by \cite{MDL_1978} states that the best model for a dataset is the one that minimizes the amount of information needed to describe it \citep{Grunwald_2009}.
MDL methods trade off goodness-of-fit against model complexity to reduce generalization error.
In the context of Bayesian networks, \cite{Friedman_1996} applied the MDL principle to determine the optimal number of discretization intervals for continuous variables and the optimal positions of their discretization edges.
Their approach selects a discretization policy that minimizes the sum of the description length of the discretized Bayesian network and the information necessary for recovering the continuous values from the discretized data.

@@

where larger values of $L$ encourage more discretization intervals.
This prior encourages edges between well-separated values over edges between closely packed samples.
All experiments set $L$ to the largest number of intervals among discrete variables in $\cX$'s Markov blanket, which encourages Bayesian networks with consistent interval counts.
In some cases it may be desirable to use higher values for $L$, such as when discrete variables are binary and the continuous variable requires higher fidelity.
